\textbf{SPECFEM3D Cartesian}\\ \textbf{User Manual}

### 2013-03-04 doc/USER_MANUAL/manual_SPECFEM3D_Cartesian.tex
more explanations about how to use PML with an external tomographic velocity and density model

>>>>

If you use PML and an external tomographic velocity and density model,
you should be careful because mathematically a PML cannot handle heterogeneities along the
normal to the PML edge inside the PML layer. This comes from the fact that the damping profile
that is defined assumes a constant velocity and density model along the normal
direction.

Thus, you need to modify your velocity and density model in order for it to be 1D inside
the PML, as shown in Figure~\ref{fig:modify_external_velocity_model_to_use_PML}.

This applies to the bottom layer as well; there you should make sure
that your model is 1D and thus constant along the vertical direction.

To summarize, only use a 3D velocity and density model inside the physical region, and in
all the PML layers extend it by continuity from its values along the
inner PML edge.

%%
\begin{figure}[htbp]
\noindent \begin{centering}
\includegraphics[width=3in]{figures/how_to_use_PML_when_a_tomographic_velocity_model_is_used.png}
\par\end{centering}
\caption{How to modify your external 3D velocity and density model in order to use PML.
Such a modification is not needed when using Stacey absorbing boundary conditions (but such conditions
are significantly less efficient).}
\label{fig:modify_external_velocity_model_to_use_PML}
\end{figure}
%%
